---
title: "Lesson 7"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(dslabs)
library(tidyverse)
library(dplyr)
```


## Part 1: Import Dataset

### Exercise 1

Fill in the blank of the following code to enable the import of inline csv file.
```{r csv1, exercise = T}
read_csv("# The first line of metadata
  # The second line of metadata
  # The third line of metadata
  # Date: 10/05/2020
  # Created by: xxxx
  x,y,z
  1,2,3", _______)
```

### Exercise 2: read csv file as name (age, race, gender)

Detail show in the below table, create a inline csv file to import those data.
```{r csv2, eval=TRUE, echo=FALSE}
read_csv("18,Black,F
         24,White,M
         36,Asia,F", c("age", "race", "gender"))

```

```{r csv3, exercise = T}
#Type your code here
```

### Exercise 3: deal with missing data

Fill in the blank of the following code to enable the import of inline csv file.
```{r csv4, exercise = T}
# the value of varible c is missing
read_csv("a,b,c
         1,2, ", __________)
read_csv("a,b,c
         1,2,.", __________)
```



## Part 2: Parsing a vector

### Exercise 1

```{r parse}
quiz(
  question("What's the type of vector when running the code: parse_logical(c(\"TRUE\", \"FALSE\", \"NA\"))",
    answer("logical", correct = TRUE),
    answer("integer"),
    answer("date"),
    answer("character")
  ),
  question("What's the type of vector when running the code: parse_character(c(\"TRUE\", \"FALSE\", \"NA\"))",
    answer("logical"),
    answer("integer"),
    answer("date"),
    answer("character", correct = TRUE)
  ),
  question("What's the type of vector when running the code: str(parse_date(c(\"2010-01-01\", \"1979-10-14\")))",
    answer("returns a warning: parsing failures"),
    answer("integer"),
    answer("date", correct = TRUE),
    answer("number")
  ),
  question("What's the type of vector when running the code: str(parse_number(c(\"2010-01-01\", \"1979-10-14\")))",
    answer("returns a warning: parsing failures"),
    answer("integer"),
    answer("date"),
    answer("number", correct = TRUE)
))
```

### Exercise 2

Fill in the blank of the following code.Read data as 324.54.
```{r num1, exercise = T}
parse_double("324,54", _______)
```

Read "This shirt costs $9.15." as a number "9.15".
```{r num2, exercise = T}
#type you code here
```

Fill in the blank of the following code. Transform "fruit_you_buy" into a factor using "fruit" as level.
```{r factor, exercise = T}
fruit <- c("apple", "banana", "watermelon", "orange")
fruit_you_buy <- c("orange", "orange", "orange", "apple","apple", "watermelon")
fruit_you_buy <- __________(fruit_you_buy, __________)
str(fruit_you_buy)
```

Fill in the blank of the following code.Read date as 2020-09-25.
```{r date, exercise = T}
parse_date("09/25/2020", "__________")
```
