---
title: "Lesson2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(dslabs)
library(dplyr)
library(tidyverse)
```


## Part 1 

### Tidyverse and ggplot2

```{r question1, echo=FALSE}
question("In order to use ggplot2, we need to reload the tidyverse package every time we start a new session.",
  answer("True", correct = TRUE),
  answer("False"),
  incorrect = "Incorrect. You only need to install a package once, but you need to reload it every time you start a new session.")
```


### Creating a scatterplot using ggplot2

*mpg* is a data frame provided by R. 
```{r, echo=TRUE}
data(mpg)
head(mpg) 
#returning the first 6 rows
```
Fill in the blanks of this code to plot *mpg* with *displ* on the x-axis and *hwy* on the y-axis.  
```{r scatterplot, exercise = TRUE}
ggplot(data =    ) + geom_point(mapping = aes(x =   , y =   ))
```
Modify this code to map *class* to the *color* aesthetic. You can run the code to see the plot.
```{r mapping1, exercise = TRUE}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, size = class))
```
Based on the code above, create a scatterplot of *mpg* with *cyl* on the x-axis and *hwy* on the y-axis, and make all of the points blue.
```{r mapping2, exercise = TRUE}
```
Use the contagious disease data for US states for the following question.
```{r, echo = TRUE}
# remember to load the package every time you start a new session
data(us_contagious_diseases)
head(us_contagious_diseases)
```
Create a scatterplot of *us_contagious_diseases* with *year* on the x-axis and *count* on the y-axis, and map *disease* to the *color* aesthetic.
```{r mapping3, exercise = TRUE}
```


### Common problem

ggplot(data = mpg)     
+ geom_point(mapping = aes(x = displ, y = hwy))
```{r question2, echo=FALSE}
question("When you run the code above, will it cause an error?",
  answer("Yes", correct = TRUE),
  answer("No"),
  incorrect = "Incorrect. + has to come at the end of the line, not the start.")
```



## Part 2

### Facets
```{r question3, echo=FALSE}
question("To facet your plot by a single varibale, you should use facet_grid().",
  answer("True"),
  answer("False", correct = TRUE),
  incorrect = "Incorrect. You should use facet_wrap() to facet plot by a single variable. facet_grid() is used to facet your plot on the combination of two variables")
```

Use the *mpg* data frame for the follwing questions.   
Complete the code to facet the plot by *class*.
```{r facet1, exercise = TRUE}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy)) + facet_wrap(    , nrow = 2)
```
Complete the code to facet the plot with *drv* on the row and *cyl* on the column.
```{r facet2, exercise = TRUE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_grid(    )
```
Use the *us_contagious_diseases* dataset for the following question.    
Create a scatterplot of *us_contagious_diseases* with *year* on the x-axis and *count* on the y-axis, and facet the plot by *disease*.
```{r facet3, exercise = TRUE}
```



### Geometric objects
Use the *mpg* dataset for the following questions.    
Modify this code so that the plot uses the smooth geom instead of the point geom, and map *drv* to linetype.
```{r geom1, exercise = TRUE}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy))
```
Modify this code to avoid repetition occured when adding multiple geom fuctions.
```{r geom2, exercise = TRUE}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  geom_smooth(mapping = aes(x = displ, y = hwy))
```
Use the *us_contagious_diseases* dataset for the following question.     
Create a plot with *year* on the x-axis and *count* on the y-axis, using the smooth geom.
```{r geom3, exercise = TRUE}
```
```{r question4, echo=FALSE}
question("If you place mappings in a geom function, ggplot2 will treat them as global mappings for all the layers.",
  answer("True"),
  answer("False", correct = TRUE),
  incorrect = "Incorrect. If you place mappings in a geom function, ggplot2 will treat them as local mappings for the layer. It will use these mappings to extend or overwrite the global mappings for that layer only. ")
```


## Part 3

### Statistical transformations
```{r question5, echo=FALSE}
question("For geom_bar(), the default value for stat is count, which maps the height of the bars to the raw values of a  
y variable.",
  answer("True"),
  answer("False", correct = TRUE),
  incorrect = "Incorrect. The default value is count, but you need to change stat to *identity* to map the height of bars to the raw values of a y variable")
```
We will use the *diamonds* dataset for the following coding questions.       
The *diamonds* dataset comes in ggplot2 and contains information about ~54,000 diamonds, including the *price*, *carat*, *color*, *clarity*, and *cut* of each diamond.
```{r, echo=TRUE}
data(diamonds)
head(diamonds) #returning the first 6 rows
```
Complete the code to create a bar chart that displays the total number of diamonds in the diamonds dataset, grouped by *cut*.
```{r stat1, exercise = TRUE}
ggplot(data = diamonds) +     (mapping = aes(x =    ))
```
Complete the code to display a bar chart of proportion instead of count.
```{r stat2, exercise = TRUE}
ggplot(data = diamonds) +     (mapping = aes(x =     , y =     , group = 1))
```
Use the *us_contagious_diseases* dataset for the following question.     
Create a bar chart that displays the total count of each type of  *disease*.
```{r stat3, exercise = TRUE}
```

### Position adjustments
```{r question6, echo = FALSE}
question("Which position adjustment is more useful for 2d geoms, like points?",
  answer("fill"),
  answer("dodge"),
  answer("identity", correct = TRUE),
  answer("jitter"),
  incorrect = ("Incorrect. The identity position adjustment is more useful for 2d geoms, like points, where it is the default.")
)
```
```{r question7, echo = FALSE}
question("Which position adjustment can make each set of stacked bars the same height?",
  answer("fill", correct = TRUE),
  answer("dodge"),
  answer("identity"),
  answer("jitter"),
  incorrect = ("Incorrect. The fill position adjustment can make each set of stacked bars the same height.")
)
```
Use *diamonds* dataset for the following coding question.     
Modify the code to map *clarity* to the fill aesthetic, and places overlapping objects directly beside one another.    
(hint: think about which position adjustment could achieve this!)
```{r pa1, exercise = TRUE}
ggplot(data = diamonds) + geom_bar(mapping = aes(x = cut, colour = cut))
```
Use *mpg* data frame for the follwing question.     
Modify the code to avoid the overplotting problem in this scatterplot.    
(hint: think about which position adjustment could achieve this!)
```{r, echo = TRUE}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy))
```
```{r pa2, exercise = TRUE}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy))
```







