---
title: "Lesson3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library("tidyverse")
```


## Part 1: Basic

### Exercise 

#### 1. Compute $\sqrt{(380 + 175 / 1.25)^2*36}$. Answer following question.

```{r com1, exercise=TRUE}
#type your code here
```

```{r com1q, echo=FALSE}
question("What is your calculated value?",
  answer("3120", correct = TRUE),
  answer("5840")
  )
```

#### 2. Variable x is already created in the environment. Please using seq() create a set of number as 3, 5, 7, 9 and store as variable y. Calculate x+y. Answer following question.

```{r com2, exercise=TRUE}
x <- c(1, 2)
#type your code here

```

```{r com2q, echo=FALSE}
question("What is your calculated value?",
  answer("4 7 8 11", correct = TRUE),
  answer("5 6 9 11"),
  incorrect = "Incorrect. y<-seq(3, 9, by=2)")

```

#### 3. Take a look at the following code.
```{r com3, eval=FALSE, echo=T}
my_variable <- 10
my_varlable
```

```{r com3q, echo=FALSE}
question("This code will cause an error",
  answer("True", correct = TRUE),
  answer("False"),
  incorrect = "Incorrect. Take a carefull look at what behind the \"my_var\" ")

```

#### 4. Correct the following R commands so that they can run correctly.(3 mistakes)

```{r com4, exercise=T}
data(mpg)
data(diamonds)

ggplot(dota = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl == 8)
filter(diamond, carat > 3)
```



## Part 2: Scripts

```{r question, echo=FALSE}
quiz( caption = "Exercise", 
  question("Which methods can create a R script file?",
    answer("File > New File > R script", correct=TRUE),
    answer("Ctrl + Shift + N", correct=TRUE), 
    incorrect = "Both are true"
  ),
  question("Which methods can run the code",
    answer("Run botton", correct=TRUE),
    answer("Cmd/Ctrl + Enter", correct=TRUE)
  ),
  question("Which of the following code will cause an error?",
    answer("x <- 10"),
    answer("xy <- 10"),
    answer("this_is_a_long_name <- 10"),
    answer("3 == NA", correct = T)
  )
)
```

## Part 3: Projects

```{r question2, echo=FALSE}
quiz( caption = "Exercise", 
  question("Which code can used to print your current working directory in R?",
    answer("getwd()", correct=TRUE),
    answer("setwd()"), 
    answer("cd()")
  ),
  question("Which is of the following is correct ",
    answer("Run botton", correct=TRUE),
    answer("Cmd/Ctrl + Enter", correct=TRUE)
  )
)
```  

#### Based on the following code we use to create a project in class:
```{r project, eval=FALSE, echo=T}
library(tidyverse)

ggplot(diamonds, aes(carat, price)) + 
  geom_hex()
ggsave("diamonds.pdf")

write_csv(diamonds, "diamonds.csv")
```


```{r question3, echo=FALSE} 
  question("Which of the following file will not in your project folder?",
    answer("diamonds.csv"),
    answer("diamonds.pdf"),
    answer("diamonds.R"),
    answer("diamonds.RData", correct = T)
  )
```
