---
title: "Lesson5"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(dslabs)
library(tidyverse)
library(dplyr)
data(mpg)
data("us_contagious_diseases")
```

## Part 1: Variation

### Exercise 

#### We will using the "mpg" dataset to continue the exercise.

```{r mpg, echo=TRUE}
glimpse(mpg)
```
For the 11 variables,

manufacturer: manufacturer name

model: model name

displ: engine displacement, in litres

year: year of manufacture

cyl: number of cylinders

trans: type of transmission

drv: the type of drive train, where f = front-wheel drive, r = rear wheel drive, 4 = 4wd

cty: city miles per gallon

hwy: highway miles per gallon

fl: fuel type

class: "type" of car

#### 1. Visualizing categorical variable - manufacturer.

Using a bar chart to present the distribution of manufacturer.

```{r mpg1, exercise=TRUE}
ggplot(  ) +
  geom_bar(   )
```

```{r mpg1q, echo=FALSE}
question("Which manufacturer has the highest count?",
  answer("dodge", correct = TRUE),
  answer("audi"),
  answer("toyota"),
  answer("volkswagen")
  )
```

#### 2. Visualizing continuous variable -  highway miles per gallon (hwy)

Using a bar chart to present the distribution of highway miles per gallon. You can try to play with different binwidth.

```{r mpg2, exercise=TRUE}
ggplot(  ) + 
  geom_histogram(  )

```

#### 3. Visualizing unusual values - highway miles per gallon (hwy)

Based on the previous histogram plot of hwy. We notice there're some unusual values. And those values are hwy > 40.
Find out those values.

```{r mpg3, exercise=T}
mpg %>%
  filter(   ) %>%
  arrange(   )

```

## Part 2: Covariation

#### 1. Categorical & continuous variable -  highway miles per gallon (hwy) vs number of cylinders(cyl)

Identify the distribution of highway miles per gallon based on differenct number of cylinders.

```{r mpg4, exercise=TRUE}
ggplot(  , aes(x=  , color=  ))+
  geom_freqpoly(  )
```

Using a *density* plot.

```{r mpg5, exercise=TRUE}
ggplot(  , aes(x=  , y=  ))+
  geom_freqpoly(aes(color =    ))
```

Using a *boxplot*.

```{r mpg6, exercise=TRUE}
ggplot(  , aes(x=  , y=  ))+
  
```

#### 2.Two Categorical variables

We want figure out whether there's any relationship between the maufacturer and the model of the car.

First, using geom_count():

```{r mpg7, exercise=TRUE}
ggplot(  )+
  geom_count(  )
```

Then, try using geom_tile():

```{r mpg8, exercise=TRUE}
mpg %>%
          %>%
ggplot(  )+
  geom_tile(  )
```

## Part3: Patterns and models

Now, we will focusing on the dataset "us_contagious_diseases".
We are curious about how will the contagious diseases case number change over the year in New York.
Try to creat a plot show this pattern.

```{r mpg9, exercise=TRUE}
us_contagious_diseases %>%
  
```

<div id="mpg9-hint">
**Hint:** You may use geom_line(), cause the count is provided in the dataset.
</div>

```{r mpg9q, echo=FALSE}
quiz( caption = "Test your result",
question("Which type of contagious disease has a highest case numbers among 1930-1960 in New York?",
  answer("Hepatitis A"),
  answer("Measles", correct = TRUE),
  answer("Mumps"),
  answer("Pertussis"),
  answer("Polio"),
  answer("Rubella"),
  answer("Smallpox")
  ),
question("Which of the pattern of the case number of Mumps throughout year in New York is correct?",
  answer("Mumps cases increase over the year in New York."),
  answer("Mumps cases decrease over the year in New York.", correct=T)
         )
)
```

