---
title: "Lesson4"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(dslabs)
library(dplyr)
library(tidyverse)
library(nycflights13)
```


## Part 1 

### Filter rows with filter()
Use *flights* data from the *nycglights13* package.
```{r, echo = TRUE}
data(flights)
head(flights)
```
Complete the code to select all flights on December 1st and save as *dec1*.
```{r filter1, exercise = TRUE}
dec1 <- filter(flights,     ,     )
dec1
```
The following code finds all flights that departed in November or December. Rewrite it using *%in%*.
```{r filter2, exercise = TRUE}
nov_dec <- filter(flights, month == 11 | month == 12)
nov_dec
```
Use the contagious disease data for US states for the following question.
```{r, echo = TRUE}
data(us_contagious_diseases)
```
Write a code to select all diseases counts in Year 2000 and save it as *yr2000*
```{r filter3, exercise = TRUE}
```

### Arrange rows with arrange()
Use *flights* for the following question.      
Complete the code to re-order *dep_delay* in ascending order.
```{r arrange1, exercise = TRUE}
arrange(    ,     )
```
Use *us_contagious_diseases* data for the following question.     
Sort *us_contagious_diseases* to find the disease with the most yearly counts among all years. (Hint: you may want to re-order *count*.)
```{r arrange2, exercise = TRUE}
```


## Part 2

### Select columns with select()
Use *flights* for the following question.      
Complete the code to select all columns, except those from year to day. (inclusive)
```{r select1, exercise = TRUE}
select(flights,      )
```

### Add new variables with mutate()
Use *flights* for the following question.      
Complete the code to add *gain* (difference between dep_delay and arr_delay), *hours* (hours sepnt in the air), and *gain_per_hour*.
```{r mutate, exercise = TRUE}
flights_sml <- select(flights, year:day, ends_with("delay"), distance, air_time)
mutate(flights_sml,
  gain =    ,
  hours =     ,
  gain_per_hour =     
)
```

## Part 3

### Grouped summaries with summarise()
Use *flights* for the following questions.    
Complete the code to group *flights* by date (year, month, day), and get the average delay per date.
```{r sum1, exercise = TRUE}
by_day <- group_by(   ,   ,    ,    )
summarise(by_day, delay =     )
```
Using %>% to rewrite the code.
```{r pipe, exercise = TRUE}
by_dest <- group_by(flights, dest)
delay <- summarise(by_dest,
  count = n(),
  dist = mean(distance, na.rm = TRUE),
  delay = mean(arr_delay, na.rm = TRUE)
)
delay <- filter(delay, count > 20, dest != "HNL")
```
Complete the code below to find the first and last departure for each day. (after removing cancelled flights)
```{r group1, exercise = TRUE}
not_cancelled <- flights %>% 
  filter(!is.na(dep_delay), !is.na(arr_delay))
not_cancelled %>% 
  group_by(     ) %>% 
  summarise(
    first_dep =    , 
    last_dep =     
  )
```
Complete the code to find out which destinations have the most carriers.
```{r group2, exercise = TRUE}
not_cancelled %>% 
  group_by(    ) %>% 
  summarise(carriers =      ) %>% 
  arrange(     )
```
Use *us_contagious_disease* for the following question.     
Write a code to find out the total counts of each disease for each year.
```{r group3, exercise = TRUE}
```








