---
title: "Lesson1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(dslabs)
library(dplyr)
```


## Part 1 

### Installation of R, RStudio and R packages

```{r question1, echo=FALSE}
quiz( caption = "Exercise", 
  question("We can use https://cloud.r-project.org to download R.",
    answer("TRUE", correct=TRUE),
    answer("FALSE")
  ),
  question("We can use http://www.rstudio.com/download to download RStudio.",
    answer("TURE", correct=TRUE),
    answer("FALSE")
  ),
  question("Which of the following code using to install packages into R will cause an error?",
    answer("install.packages(\"tidyverse\")"),
    answer("install.packages(tidyverse)", correct = T),
    answer("install.packages(c(\"gapminder\", \"readr\", \"broom\"))"),
    answer("install.packages(\'tidyverse\')")
  )
)
```

## Part 2

### Running R Code 

Lets have a try:

```{r code, exercise=TRUE}
1 + 2
1 / 3
3 * 4
sum(3, 4)
```

### Getting help from R

*mtcars* is a dataset provided by R.

```{r, echo=TRUE}
data(mtcars)
head(mtcars) #returning the first 6 rows
```

Suppose you want to kown more about what each column in this dataset present, what should you do?
```{r help, exercise=TRUE}
#type your code here
```

<div id="help-hint">
**Hint:** You may use the help function in R.
</div>

## Part 3

### Introduction of a public health data: Contagious disease data for US states

#### Usage
```{r, echo=TRUE}
#dataset stored in dslabs package, remember to install the package when using on your own RStudio
#install.packages("dslabs")
#library(dslabs)
data(us_contagious_diseases)
```

```{r datahelp, exercise=TRUE}
#if you need more information using
?us_contagious_diseases
```

#### Overview the dataset
```{r overview, echo=TRUE}
head(us_contagious_diseases)
glimpse(us_contagious_diseases) #function in dplyr package
```

```{r question2, echo=FALSE}
question("How many variables are in this dataset ?",
  answer("6", correct = TRUE),
  answer("16,065"),
  incorrect = "Incorrect. There are 6 variables and 16,065 observations in this dataset.")

```


