---
title: "Lesson6"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
library(dslabs)
library(dplyr)
library(tidyverse)
```

## Part 1

### Creating tibbles

```{r q1, echo = FALSE}
question("Which is the correct way to coerce data frame iris to a tibble?",
         answer("tibble(iris)"),
         answer("as_tibble(iris)", correct = TRUE),
         answer("tribble(iris)"),
         incorrect = "Incorrect, you should use as_tibble() to coerce a data frame to a tibble."
)
```

tb <- tibble(    
  :) = "smile",     
  2000 = "number"    
)
```{r q2, echo = FALSE}
question("When you run the code above, will it cause an error?",
         answer("Yes", correct = TRUE),
         answer("No"),
         incorrect = "Incorrect, for a tibble to have non-syntactic variable names, you need to surround them with backticks, `."
)
```

Create a tibble with x from 1 to 10, y = 2*x, and z = (x+y)^2.
```{r tibble1, exercise = TRUE}

```

```{r, echo = TRUE}
# A tibble: 3 x 3
#  a         b     c
#  <chr> <dbl> <dbl>
#  x         7   5.5
#  y         8   9.7
#  z         9  10.8
```
Write a code to create a tibble with above results.
```{r tibble2, exercise = TRUE}
```


## Part 2

### Printing
```{r, eval = FALSE, echo = TRUE}
nycflights13::flights %>% 
  print(n = 10, width = Inf)
```
```{r q3, echo = FALSE}
question("How many rows and columns will the above code print?",
         answer("10 rows and 10 columns"),
         answer("10 rows and all coloumns", correct = TRUE),
         answer("all rows and 10 columns"),
         answer("all rows and all columns"),
         incorrect = "Incorrect, it will print 10 rows and all columns."
)
```

```{r, eval = FALSE, echo = TRUE}
options(tibble.print_max = n, tibble.print_min = m)
```
```{r q4, echo = FALSE}
question("What will the above code do?",
         answer("If more than n rows, print only m rows", correct = TRUE),
         answer("If more than m rows, print only n rows"),
         answer("If more than n columns, print only m columns"),
         answer("If more than m columns, print only n columns"),
         incorrect = "Incorrect, if more than n rows, it will print only m rows."
)
```

Use *flights* for the following question.     
Write a code to print 8 rows and all columns of *flights*.
```{r print, exercise = TRUE}
```


## Part 3

### Subsetting

Use *us_contagious_disease* for the following question.     
Write a code to extract *disease* from the dataset.
```{r subset1, exercise = TRUE}
```
Write a code to extract the third variable in the dataset.
```{r subset2, exercise = TRUE}
```













